Active Learning Benchmark

### 2023-01-31 doc/research_presentation/research_presentation.tex
cifar10 preliminary tests
presentation

\begin{frame}[fragile]{Scope}
	The framework is planned to include
	\begin{itemize}
		\item Three different domains (Tabular, Image, Text)
		\item SOTA baseline methods 
		\item Preprocessed datasets (train/test split and seed set)
		\item Tuned classifiers for each dataset
		\item Set logging and evaluation procedures
		\item (Single Domain and Domain Transfer use cases)
	\end{itemize}
	The framework will \textbf{not} include
	\begin{itemize}
		\item Batch Active Learning
		\item Elaborate Training (Data Augmentation, etc.)
	\end{itemize}
\end{frame}

@@

\begin{frame}[fragile]{Cross Validation}
	\begin{figure}
		\centering
		\includegraphics[width=.7\linewidth]{pics/splice_margin100_convergence.jpg}
	\end{figure}
\end{frame}

@@

\begin{frame}[fragile]{Single Domain vs. Transfer}
	pass
\end{frame}

@@

\begin{frame}[fragile]{Classifier Training}
	Labeled points are unweighted

	Always at least one epoch of training

	Aggressive early stopping with patience $0$

	Adam (NAdam) optimizer, since SGD proves to be too slow (needs more epochs)
\end{frame}

>>>>

\begin{frame}[fragile]{Scope}
	The framework is planned to include
	\begin{itemize}
		\item Three different domains (Tabular, Image, Text)
		\item SOTA baseline methods 
		\item Preprocessed datasets (train/test split and seed set)
		\item Tuned classifiers for each dataset
		\item Set logging and evaluation procedures
		\item (Ensemble Approaches)
		\item (Single Domain and Domain-Transfer use cases)
	\end{itemize}
	The framework will \textbf{not} include
	\begin{itemize}
		\item Batch Active Learning
		\item Elaborate Training (Data Augmentation, etc.)
	\end{itemize}
\end{frame}

@@

\begin{frame}[fragile]{Cross Validation}
	\begin{figure}
		\centering
		\includegraphics[width=.7\linewidth]{pics/splice_margin100_convergence.jpg}
		\caption*{Uncertainty Sampling}
	\end{figure}
\end{frame}

@@

\begin{frame}[fragile]{Ensemble Approaches}
	Uncertainty Sampling profits a lot from ensembles

	The logical thing is to build the final classifier as an ensemble \\ [7mm]
	%
	How do you compare single model approaches to ensemble approaches?

	Prefix a single evaluation model out of the ensemble?
\end{frame}

\begin{frame}[fragile]{Single Domain vs. Transfer}
	Single Domain: Fit AL agent on the same dataset that you evaluate on (not useful in practice)

	Domain Transfer: Fit AL agent on domain with large resources and evaluate agent on domain with few resources

	Often used in NLP (fit agent on English data and evaluate for Spanish / German)
\end{frame}

@@

\begin{frame}[fragile]{Classifier Training}
	\begin{table}
		\centering
		\begin{tabular}{l || l}
			\textbf{General Setup} & \textbf{Speed Optimizations} \\
			\hline
			Cross-Entropy Loss & Fine tuning \\ [1mm]
			No case weights & Agressive Early Stopping \\[1mm]
			At least one epoch & \\[1mm]
			NAdam optimizer &
		\end{tabular}
	\end{table}
\end{frame}

\begin{frame}[fragile]{Some Results}
	\begin{table}
		\centering
		\begin{tabular}{l || c | c }
			\textbf{Agent} & \textbf{Acc} & \textbf{AUC} \\
			\hline
			Oracle & 0.8806 $\pm$ 0.0141 & 0.8530 $\pm$ 0.0132 \\
			SAR & 0.8839 $\pm$ 0.0142 & 0.8339 $\pm$ 0.0118 \\
			Margin & 0.8849 $\pm$ 0.0112 & 0.8309 $\pm$ 0.0141 \\
			Entropy & 0.8822 $\pm$ 0.0156 & 0.8285 $\pm$ 0.0154 \\
			Coreset & 0.8788 $\pm$ 0.0105 & 0.8246 $\pm$ 0.0108 \\
			Random & 0.8744 $\pm$ 0.0144 & 0.8152 $\pm$ 0.0129
		\end{tabular}
		\caption*{Results for Splice}
	\end{table}
\end{frame}
